\documentclass{article}
\usepackage[skip=10pt]{parskip}
\usepackage{amsmath}
\usepackage{amssymb}
\begin{document}

3a. The base case is for $n = 1$, where we see the inequality obviously holds true because $1! > (1 / e)^1$. If we assume the inequality to hold true for $n$, then we are left to prove the inequality true for $n + 1$.

\begin{align*}
    (n + 1)! &= (n + 1)n! \\
    (n + 1)! &> (n + 1)(n / e)^n \\
\end{align*}

Multiplying numerator and denominotor on the RHS by $(n + 1)^n$, we get

\begin{align*}
    (n + 1)! &> (n + 1)^{n + 1} (n / (n + 1))^n  / e^n \\
    (n + 1)! &> (n + 1)^{n + 1} (1 / (1 + 1 / n)^n) / e^n \\
\end{align*}

Now, since $e > (1 + 1 / n)^n$ for all $n$, we get

\begin{align*}
    (n + 1)! &> (n + 1)^{n + 1} (1 / e) / e^n \\
    (n + 1)! &> (n + 1)^{n + 1} / e^{n + 1} \\
    (n + 1)! &> ((n + 1) / e)^{n + 1} \\
\end{align*}

This concludes the proof by induction. Let's now prove by construction (although not asked for in the exercise).

Consider the following expansion of $n!e^n$.

\[ n!e^n = \prod_{k=1}^n ke \]

We are now going to replace each of the $e$'s with an inequality based on the fact that $e > (1 + 1 / r)^r$ for all positive integers $r$.

\begin{align*}
    n!e^n &> \prod_{k=1}^n k(1 + 1 /k)^k \\
    n!e^n &> \prod_{k=1}^n (k + 1)^k / k^{k - 1}
\end{align*}

We can now cancel each of the denominators on the RHS with the preceding numerator, and obtain

\begin{align*}
    n!e^n &> (n + 1)^n \\
    n!e^n &> n^n \\
    \therefore n! &> (n / e)^n
\end{align*}

This concludes the proof.

3b. We'll apply the arithmetico-geometric inequality on the set of integers ${1, 2, 3, ..., n}$. This gives us

\begin{align*}
    \sqrt[n]{\prod_{k = 1}^n k} &< (\sum_{k = 1}^n k) / n \\
    \sqrt[n]{n!} &< (n(n + 1) / 2) / n \\
    n! &< ((n + 1) / 2)^n
\end{align*}

Multiplying numerator and denominator on the RHS by $n^n$, we get

\begin{align*}
    n! &< ((n + 1) / n)^n (n / 2)^n \\
    n! &< (1 + 1 / n)^n (n / 2)^n
\end{align*}

Once again, since $e > (1 + 1 / n)^n$ for all $n$, we get the desired result $n! < e(n / 2)^n$.



\end{document}
